Analysis of Shootings and Firearm Discharges in Toronto

### 2024-11-30 paper/paper.qmd
plots adjustment

ggplot(analysis_data, aes(x = neighbourhood_158, y = weighted_score, fill = neighbourhood_158)) +
  geom_bar(stat = "identity") +
  labs(title = "Weighted Score by Neighbourhood", x = "Neighbourhood", y = "Weighted Score") +
  theme_minimal() +
  theme(axis.text.x = element_blank())

>>>>

ggplot(analysis_data, aes(x = neighbourhood_158, y = weighted_score, fill = neighbourhood_158)) +
  geom_bar(stat = "identity") +
  labs(title = "Weighted Score by Neighbourhood", x = "Neighbourhood", y = "Weighted Score") +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle=90, vjust=0.5, hjust=1, size=5))
